Narrative

### 2023-05-25 manuscript/manuscript.qmd
results: added some dynamic results

For all heterogeneity levels in Figure 1 above zero we see an overall underestimate of heterogeneity due to unreliability in primary studies. This negative bias can be relatively severe, is worse with lower effect size and lower average reliability, and worsens in an absolute sense but improves in a relative sense as heterogeneity increases. For example, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.1$, the bias is `r in_text$bias_increasing_tau$tau_0.1` for Pearson's $r$, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.15$ the bias is `r in_text$bias_increasing_tau$tau_0.15`, and for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.2$ the bias is `r in_text$bias_increasing_tau$tau_0.2`.

>>>>

For all heterogeneity levels in Figure 1 above zero we see an overall underestimate of heterogeneity due to unreliability in primary studies. This negative bias can be relatively severe, is worse with lower effect size and lower average reliability, and worsens in an absolute sense but improves in a relative sense as heterogeneity increases. For example, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.1$, the bias is `r in_text$bias_increasing_tau$tau_0.1` for Pearson's $r$, for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.15$ the bias is `r in_text$bias_increasing_tau$tau_0.15`, and for $\bar{R} = 0.8$, $\mu = 0.2$, $\tau = 0.2$ the bias is `r in_text$bias_increasing_tau$tau_0.2`. For an effect size of $\mu = 0.2$ true heterogeneity between 0.1 - 0.2 is underestimated by between `r round(100*in_text$underestimate_mu02$underestimate_min$underestimate, 0)`% ($\tau = 0.2$, $\bar{R} = 0.9$) and `r round(100*in_text$underestimate_mu02$underestimate_max$underestimate, 0)`% ($\tau = 0.1$, $\bar{R} = 0.6$).
